---
title: "Energy Intensity Data"
subtitle: "Introduction"
author: "Andrew Holguin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Energy Intensity}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

The `energyintensity` R package provides classes and functions to support the
development of network-based energy intensity models using utility meter and
infrastructure data. It is currently only available on Github:

```{r eval=FALSE}
remotes::install_github("ucd-cwee/energyintensity")
```

```{r}
library("energyintensity")
```

The basic data required to build a spatially disaggregeted energy intensity
model can be divided into two main categories:

1. asset-level data (typically readings from water and energy meters)  
2. network connectivity model  

With data of these two types, it is possible to model the cumulative energy
required to serve different locations within the water utility distribution
network.

Other types of data can also be integrated, both to improve the robustness of
the model and to enable additional analytical features. These include spatial
pressure zones, customer consumption data, and modeled flow values (e.g., from a
hydraulic model).


## Asset Meter Data

Asset water meter data is typically obtained either from a utility SCADA system,
which measures flow rates at regular intervals, or from aggregated records
provided by the water utility. Energy meter data is similarly obtained from the
water utility SCADA system, or as is often the case, from energy utility billing
records. The data for each meter is structured as a time series, however the
measurment resolution (e.g., regular 15-minute interval vs. irregular billing
cycles) and type (e.g., rate vs. volume) may vary between the series. These
issues and others, are discussed in greater detail in the vignette on [Model
Development](model_development.html).

### Meter Data Frames

The `energyintensity` package provides a `meter_df` class, which extends the
base `data.frame` class with simple data validation, error checking, and
visualization methods. A `meter_df` object is essentially a `data.frame` with
one or more special fields added. These special fields fall into two categories:

1. time index  
2. measured values  

A `meter_df` should have exactly one time index. It may consist of either point
timestamps (see `?POSIXt`), or time intervals with both a beginning and end
point (see `??lubridate::interval`).

The `meter_df` can have any number of measured values, although in practice
there should probably be at least one. The main requirent of the measured value
fields is that they must have units explicity set (see `?units::units` and [unit
configuration](model_development.html#unit-configuration)).

Finally, any number of other ordinary fields can be included.

```{r}
library("lubridate")
library("units")

# create 
x <- meter_df(time = seq.Date(as.Date("2013-1-1"),
                              by = "+1 month",
                              length.out = 12),
              value = set_units(rnorm(12), kW))

# print
x
```

```{r}
# plot
plot(x)
```

When multiple meter data frames are merged together (see [Meter Data
Reconciliation](model_development.html#Meter-Data-Reconciliation)), additional
attributes are attached, containing information that is useful for diagnostics
and quality control.

_Why extend `data.frame`, rather than a time series object?_

The decision to base development around the `data.frame` was because of its
flexibility, and due to the wide range of tools available for working with and
manipulating them. I particular, time interval data, such as water or energy
usage measured over a billing interval (e.g., 1.3 kWh used from Jan 12 - Feb 7)
is often encountered in the development of energy intensity models. The common
time series classes in R, such as `ts`, `zoo`, and `xts` do not support time
interval data well. Future work may consider supporting other classes such as
these.

Currently, all of the modeling functions in `energyintensity` will also take
normal `data.frame` objects, as long as they follows the same basic structure.

### Using `ggplot2`

If you prefer, `ggplot2` can be used for plotting, however it does not currently
support `units`. You can either convert the values to numeric, or load the
`ggforce` package, which will enable support for `units`.

```{r message = FALSE, warning = FALSE}
library("ggforce")   # support for 'units'
library("ggstance")  # geom_linerangeh (horizontal line intervals)

ggplot(pst1_water, aes(xmin = int_start(interval),
                       xmax = int_end(interval),
                       y = water)) +
  geom_linerangeh()
```


## Network Connectivity Model

- ei_net
  - igraph with ei_data attached at nodes (and edges)
- convert between spatial and igraph-based network


## Data Integration

- associate meter data with specific nodes or edges in the graph



## Customer Data






