---
title: "Energy Intensity"
author: "Andrew Holguin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Energy Intensity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `energyintensity` R package provides classes and functions to support the
development of network-based energy intensity models using utility
meter and infrastructure data. It is currently available only on Github:

```{r eval=FALSE}
if (!require(energyintensity)) remotes::install_github("ucd-cwee/energyintensity")

```

The basic data required to build a spatially disaggregeted energy intensity
model can be divided into two categories:

1. asset water and energy meter readings  
2. network connectivity model  

With these two data sets, it is possible to model the cumulative energy required
to serve different locations within the water utility distribution network.

Other types of data can also be integrated, both to improve the robustness of
the model and to enable additional analytical features. These include spatial
pressure zones, customer consumption data, and modeled flow values (from a
hydraulic model).


### Asset Meter Data

Asset water meter data is typically obtained either from a utility SCADA system,
which measures flow rates at regular intervals, or from aggregated records
provided by the water utility. Energy meter data is similarly obtained from the
water utiilty SCADA system, or as is often the case, from energy utility billing
records. The data for each meter is structured as a time series, however the
measurment resolution (e.g., regular 15-minute interval vs. irregular billing
cycles) and type (e.g., rate vs. volume) may vary between the series.
Calculating energy intensity requires all of the water and energy meter data
associated with an asset to be combined and reconciled.

```{r}
# load sample meter data (data frame)


# plot (ggplot)


```

Cleaning and pre-processing of the data can be handled entirely by the analyst,
however, there are a few approaches built in to the `energyintensity` package,
which implement commonly used methods. These methods are used to standardize the
different time series, so that they can be merged and aggregated. The available
methods fall into two general categories: (1) aggregation, and (2) resampling.

```{r}

```






- ei_data
  - df with several specific fields

- support point and interval measurements (and conversion)
- time series vis & diagnostics
- app to support review and validation


### Network Connectivity Model

- ei_net
  - igraph with ei_data attached at nodes (and edges)

- convert between spatial and igraph-based network
- display (and edit?) connectivity


### Data Integration

- associate meter data with specific nodes or edges in the graph


### Network Time Slices

- snapshot of model during a point or interval of time
- cumulative flow and related diagnostics


### Model Execution

- calc ei & flow


### Spatial Visualization

- plot as map
- pressure zone data --> visualize ei throughout service territory


### Customer Data & Conservation Estimates




### Data Fusion & Model Tuning




### Future Development Plans

Split non-core components into other packages:
  - random data generation for simulation and testing
  - model development vis app
  - additional extensions?

- network skeletonization
- integration with external hydraulic models
- better representation of time lags and storage
- additional and improved analytical tools
- more tests, documentation, etc.



